%
%       --- acknow.tex ---
%
% Acknowledgements

\chapter*{{\Huge Acknowledgements}}

My foremost acknowledgements go to Chris Conselice for guiding and supporting the research in this thesis from start to finish. I am grateful for the freedom i've had to explore my own ideas as well as the fantastic discussion, help and feedback throughout my PhD. I would also like to thank all of the staff within the department, all of whom have contributed with advice or help in at least some small way to the work in this thesis.

This work couldn't have been done without my collaborators and colleagues both near and far. From Nottingham, a special thanks goes to Will Hartley, Alice Mortlock, Jamie Ownsworth and Carl Mundy. From farther afield, i'd like to thank Harry Ferguson for immeasurable help and advice as well as those who offered help or advice, including but not by no means limited to Romeel Dav\"{e}, Brant Robertson, Mark Dickinson, Yu Lu and Matt Ashby.

A big thank you to my officemates through the years, I couldn't have asked for a nicer set of people to keep me company every day. To the friends I made in Nottingham, your company, humour, alcohol and sugary baked goods meant more to me than you realise or would ever have been admitted to in person. Thank you all for a fantastic four years. A special mention however should go to Emma Bradshaw, who I credit with helping to bring me to Nottingham and for being a great friend and colleague while there as well.

Finally and most importantly, I wouldn't have gotten to where I am without the love and support of my family. This thesis is dedicated to you.

\clearpage

%%
%% End of file...
%%
